A Rapid Feasibility Checking for Reconfiguration of Mismatched PV Arrays

### 2019-11-25 PVSC-46/Manuscript/PVSC_Manuscript.tex
modified by comment of PVSC publisher
• Table Captions (formatting) - Table captions should be in capital letters, roman numbered and placed above the table. Captions should be fully justified.

• Table Captions (alignment) - Table captions must be centered and fully justified.

• Figure Captions (alignment) - Figure captions must be fully justified and aligned left. Change alignment for Fig 1 ,2 and 3.
fix errors
Updates from Overleaf

%\input epsf
\usepackage{graphicx}
%\usepackage[dvipdfmx]{graphicx} % for michiko
\usepackage{hyperref} 
%\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[super]{nth}
\usepackage{multicol}
% Add by Zhao
\usepackage{cite}
\usepackage{amsthm,amsfonts}
\usepackage{xcolor,color}
%\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage[utf8]{inputenc}
\usepackage[ruled]{algorithm2e}
\usepackage[colorinlistoftodos]{todonotes}
\newtheorem{definition}{Definition}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

@@

Though several reconfiguration methods have been proposed, most works consider reconfiguration in PV cell or PV module level \cite{nguyen2008adaptive,wang2014architecture,storey2013improved,storey2014optimized,udenze2018reconfiguration}. 
However, cell level reconfiguration requires a significantly high computation time and a large number of switches for reconfiguration. 
In addition, they require a special PV panels with capability of switching, and cannot be applied to the system constructed with standard PV panels. 
From a practical view, reconfiguration of connection among PV panels is a realistic solution since a PV panel is manufactured as a physical one panel with two terminals and PV panels can be flexibly interconnected. 
\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\linewidth]{../fig/compare.png}
    \caption{Power generation before and after reconfiguration}
    \label{compare}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\linewidth]{../fig/module.png}
    \caption{PV array, string, module and panel}
    \label{model}
\end{figure}

\begin{figure}
     \centering
    \begin{subfigure}[b]{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{../fig/m_1.png}
        \caption{PV module 1}
     \end{subfigure}
     \begin{subfigure}[b]{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{../fig/m_2.png}
        \caption{PV module 2}
     \end{subfigure}
     \begin{subfigure}[b]{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{../fig/m_3.png}
        \caption{PV module 3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\linewidth}
        \centering
        \vspace{3mm}
        \includegraphics[width=\linewidth]{../fig/panel.png}
        \caption{PV panel}
    \end{subfigure}
    \caption{I-V characteristics}
    \label{fig:IV}
\end{figure}

@@

\begin{table}[t]
% \caption{Extracted currents of MPPs}
% \caption{EXTRACTED CURRENTS OF MPPS}
% \label{tab:monitored}
\centering
\caption{EXTRACTED CURRENTS OF MPPS}
\begin{tabular}{c|rrrr}
\hline\hline
       &    	\multicolumn{4}{c}{Panels}								\\
	&	\multicolumn{1}{c}{$P1$}	&	\multicolumn{1}{c}{$P2$}	&	\multicolumn{1}{c}{$P3$}	&	\multicolumn{1}{c}{$P4$}	\\ \hline
MPP1	&	3.10A	&	3.09A	&	0.52A	&	2.47A	\\ \hline
MPP2	&	2.98A	&	2.55A	&	0.50A	&	1.53A	\\ \hline
MPP3	&	1.55A	&	2.48A	&	0.46A	&	0.48A	\\ \hline
\end{tabular}
\label{tab:monitored}
\end{table}

\begin{table}[t]
% \caption{Approximated currents of MPPs}
% \caption{APPROXIMATED CURRENTS OF MPPS}
% \label{tab:approximated}
\centering
\caption{APPROXIMATED CURRENTS OF MPPS}
\begin{tabular}{c|rrrr}	
\hline\hline
       &    	\multicolumn{4}{c}{Panels}	\\
	&	\multicolumn{1}{c}{$P1$}	&	\multicolumn{1}{c}{$P2$}	&	\multicolumn{1}{c}{$P3$}	&	\multicolumn{1}{c}{$P4$}	\\ \hline
MPP1	&	3A	&	3A	&	0.5A	&	2.5A	\\ \hline
MPP2	&	3A	&	2.5A	&	0.5A	&	1.5A	\\ \hline
MPP3	&	1.5A	&	2.5A	&	0.5A	&	0.5A	\\ \hline
\end{tabular}
\label{tab:approximated}
\end{table}

\begin{table}[t]
% \caption{Maximum number of active modules}
% \caption{MAXIMUM NUMBER OF ACTIVE MODULES}
% \label{tab:modules}
\centering
\caption{MAXIMUM NUMBER OF ACTIVE MODULES}
\begin{tabular}{c|rrrr|r}	
\hline\hline
       &    	\multicolumn{4}{c|}{Panels}	& \\									
	&	\multicolumn{1}{c}{$P1$}	&	\multicolumn{1}{c}{$P2$}	&	\multicolumn{1}{c}{$P3$}	&	\multicolumn{1}{c}{$P4$} &	\multicolumn{1}{|c}{total}	\\ \hline
3A	&	2	&	1	&	0	&	0 & 3	\\ \hline
2.5A	&	2	&	3	&	0	&	1 & 6	\\ \hline
1.5A	&	3	&	3	&	0	&	2 & 8	\\ \hline
0.5A	&	3	&	3	&	3	&	3 & 12	\\ \hline
\end{tabular}
\label{tab:modules}
\end{table}

@@

\begin{table*}[t]
% \caption{Approximated power}
\caption{APPROXIMATED POWER}
\label{tab:powers}
\centering
\begin{tabular}{c|rrrrrrrrrrr}
\hline\hline	
\# modules & 	\multicolumn{10}{c}{currents sequence for strings (A)} \\ 																
per string		&	\multicolumn{1}{c}{(3,3)}	&	\multicolumn{1}{c}{(3,2.5)}	&	\multicolumn{1}{c}{(3,1.5)}	&	\multicolumn{1}{c}{(3,0.5)}	&	\multicolumn{1}{c}{(2.5,2.5)}	&	\multicolumn{1}{c}{(2.5,1.5)}	&	\multicolumn{1}{c}{(2.5,0.5)}	&	\multicolumn{1}{c}{(1.5,1.5)}	&	\multicolumn{1}{c}{(1.5,0.5)}	&	\multicolumn{1}{c}{(0.5,0.5)}	\\ \hline
	1	&	120W	&	110W	&	90W	&	70W	&	100W	&	80W	&	60W	&	60W	&	40W	&	20W	\\ \hline
	2	&	-	&	220W	&	180W	&	140W	&	200W	&	160W	&	120W	&	120W	&	80W	&	40W	\\ \hline	3	&	-	&\textbf{330W}&	270W	&	210W	&	\textbf{300W}	&	240W	&	180W	&	180W	&	120W	&	60W	\\ \hline
4	&	-	&	-	&	-	&	-	&	-	&	\textbf{320W}	&	240W	&	240W	&	160W	&	80W	\\ \hline
	 5	&	-	&	-	&	-	&	-	&	-	&	-	&	\textbf{300W}	&	-	&	200W	&	100W	\\ \hline
	6	&	-	&	-	&	-	&	-	&	-	&	-	&	-	&	-	&	240W	&	120W	\\ \hline
\end{tabular}
\end{table*}

@@

\begin{table}[t]
% \caption{An example of the proposed method ($m = 5$)}
\caption{AN EXAMPLE OF THE PROPOSED METHOD ($ m = 5$)}
\begin{center}
\begin{tabular}{c|c|ccccc|c}\hline \hline
                               & \multicolumn{7}{c}{Panels}  \\
                               &  \multicolumn{1}{c}{$P1$}    & $P2$   & $P3$    & $P4$    & $P5$   & \multicolumn{1}{c}{$P6$}            & $P7$             \\ \hline
$M_{p}(Q_1)$        & 1     & 1     & 1     & 1     & 2    & 2    & 1              \\ \hline
$M_{p}(Q_2)$        & 1     & 2     & 2     & 2     & 3    & 3    & 2              \\ \hline
$M_{p}(Q_3)$        & 1     & 2     & 2     & 2     & 3    & 3    & 3              \\ \hline
$Loss(p,2)$           & 0     & 1     & 1     & 1     & 1    & 1    & 1    \\ \hline
$Loss(p,3)$           & 0     & 0     & 0     & 0     & 0    & 0    & 1    \\ \hline\hline
step 2        & $\surd$ & $\surd$ &$\surd$ &$\surd$ &$\surd$ & & \\ \hline
step 3      & $\surd$ & $\surd$ &$\surd$ & &$\surd$ & & \\ \hline
step 4       & $\surd$ &  & & &$\surd$ & $\surd$ & \\ \hline         
\end{tabular}
\end{center}
\label{tab:proposed-example}
\end{table}

@@

\begin{table}[ht]
% \caption{Swap rule}
\caption{SWAP RULE}
\label{tab:swap}
\centering
\begin{tabular}{c|c}
\hline\hline
\multicolumn{2}{c}{The numbers of active modules} \\
selected panels & unselected panels \\ \hline
1, 1, 1 & 3 \\ \hline
1, 1 & 2 \\ \hline
1, 2 & 3 \\ \hline
\end{tabular}
\end{table}

@@

\michiko{To evaluate the proposed method, we prepared MPP informations of 100 mismatched PV arrays and applied our algorithm. We also applied an exhaustive searching algorithm for comparison.
MPP information is setup as follows for each PV array. 
Each PV array has 6 - 24  panels and the number of PV panels is randomly determined. 
Three current values are randomly assigned to the three modules in each panel from 3 - 8 current values, where the number of possible current values are also randomly determined for each PV array.
% \zhao{\large \textbf{Is that means: Current value for PV modules in each PV panel are randomly assigned from 3 - 8 current values.}}
The number of strings after reconfiguration is 3 - 6 and it is randomly determined for each PV array.}

>>>>

%\input epsf
\usepackage{graphicx}
%\usepackage[dvipdfmx]{graphicx} % for michiko
\usepackage{hyperref} 
%\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[super]{nth}
\usepackage{multicol}
% Add by Zhao
\usepackage{cite}
\usepackage{amsthm,amsfonts}
\usepackage{xcolor,color}
% \usepackage{caption2}
%\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage[utf8]{inputenc}
\usepackage[ruled]{algorithm2e}
\usepackage[colorinlistoftodos]{todonotes}
\newtheorem{definition}{Definition}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\captionsetup[subfigure]{justification=justified,singlelinecheck=false}
\captionsetup[figure]{justification=justified,singlelinecheck=false}

@@

Though several reconfiguration methods have been proposed, most works consider reconfiguration in PV cell or PV module level \cite{nguyen2008adaptive,wang2014architecture,storey2013improved,storey2014optimized,udenze2018reconfiguration}. 
However, cell level reconfiguration requires a significantly high computation time and a large number of switches for reconfiguration. 
In addition, they require a special PV panels with capability of switching, and cannot be applied to the system constructed with standard PV panels. 
From a practical view, reconfiguration of connection among PV panels is a realistic solution since a PV panel is manufactured as a physical one panel with two terminals and PV panels can be flexibly interconnected. 
\begin{figure}[t]
\centering
\includegraphics[width=9cm]{../fig/compare.png}
% \captionstyle{flushleft}
\caption{Power generation before and after reconfiguration}
\label{compare}
\end{figure}

@@

\begin{figure}[]
    \centering
    \includegraphics[width=9cm]{../fig/module.png}
    \caption{PV array, string, module and panel}
    \label{model}
\end{figure}

\begin{figure}
     \centering
    \begin{subfigure}[b]{2.7cm}
        \centering
        \includegraphics[width=\linewidth]{../fig/m_1.png}
        \caption{PV module 1}
     \end{subfigure}
     \begin{subfigure}[b]{2.7cm}
        \centering
        \includegraphics[width=\linewidth]{../fig/m_2.png}
        \caption{PV module 2}
     \end{subfigure}
     \begin{subfigure}[b]{2.7cm}
        \centering
        \includegraphics[width=\linewidth]{../fig/m_3.png}
        \caption{PV module 3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{9cm}
        \centering
        \vspace{3mm}
        \includegraphics[width=9cm]{../fig/panel.png}
        \caption{PV panel}
    \end{subfigure}
    \caption{I-V characteristics}
    \label{fig:IV}
\end{figure}

@@

\begin{table}[t]
% \caption{Extracted currents of MPPs}
% \caption{EXTRACTED CURRENTS OF MPPS}
% \label{tab:monitored}
\centering
\caption{}
\centerline{EXTRACTED CURRENTS OF MPPS}
\vskip5pt
\begin{tabular}{c|rrrr}
\hline\hline
       &    	\multicolumn{4}{c}{Panels}								\\
	&	\multicolumn{1}{c}{$P1$}	&	\multicolumn{1}{c}{$P2$}	&	\multicolumn{1}{c}{$P3$}	&	\multicolumn{1}{c}{$P4$}	\\ \hline
MPP1	&	3.10A	&	3.09A	&	0.52A	&	2.47A	\\ \hline
MPP2	&	2.98A	&	2.55A	&	0.50A	&	1.53A	\\ \hline
MPP3	&	1.55A	&	2.48A	&	0.46A	&	0.48A	\\ \hline
\end{tabular}
\label{tab:monitored}
\end{table}

\begin{table}[t]
% \caption{Approximated currents of MPPs}
% \caption{APPROXIMATED CURRENTS OF MPPS}
% \label{tab:approximated}
\centering
\caption{}
\centerline{APPROXIMATED CURRENTS OF MPPS}
\vskip5pt
\begin{tabular}{c|rrrr}	
\hline\hline
       &    	\multicolumn{4}{c}{Panels}	\\
	&	\multicolumn{1}{c}{$P1$}	&	\multicolumn{1}{c}{$P2$}	&	\multicolumn{1}{c}{$P3$}	&	\multicolumn{1}{c}{$P4$}	\\ \hline
MPP1	&	3A	&	3A	&	0.5A	&	2.5A	\\ \hline
MPP2	&	3A	&	2.5A	&	0.5A	&	1.5A	\\ \hline
MPP3	&	1.5A	&	2.5A	&	0.5A	&	0.5A	\\ \hline
\end{tabular}
\label{tab:approximated}
\end{table}

\begin{table}[t]
% \caption{Maximum number of active modules}
% \caption{MAXIMUM NUMBER OF ACTIVE MODULES}
% \label{tab:modules}
\centering
\caption{}
\centerline{MAXIMUM NUMBER OF ACTIVE MODULES}
\vskip5pt
\begin{tabular}{c|rrrr|r}	
\hline\hline
       &    	\multicolumn{4}{c|}{Panels}	& \\									
	&	\multicolumn{1}{c}{$P1$}	&	\multicolumn{1}{c}{$P2$}	&	\multicolumn{1}{c}{$P3$}	&	\multicolumn{1}{c}{$P4$} &	\multicolumn{1}{|c}{total}	\\ \hline
3A	&	2	&	1	&	0	&	0 & 3	\\ \hline
2.5A	&	2	&	3	&	0	&	1 & 6	\\ \hline
1.5A	&	3	&	3	&	0	&	2 & 8	\\ \hline
0.5A	&	3	&	3	&	3	&	3 & 12	\\ \hline
\end{tabular}
\label{tab:modules}
\end{table}

@@

\begin{table*}[t]
% \caption{Approximated power}
  \caption{}
  \centerline{APPROXIMATED POWER}
  \vskip5pt
\label{tab:powers}
\centering
\begin{tabular}{c|rrrrrrrrrrr}
\hline\hline	
\# modules & 	\multicolumn{10}{c}{currents sequence for strings (A)} \\ 																
per string		&	\multicolumn{1}{c}{(3,3)}	&	\multicolumn{1}{c}{(3,2.5)}	&	\multicolumn{1}{c}{(3,1.5)}	&	\multicolumn{1}{c}{(3,0.5)}	&	\multicolumn{1}{c}{(2.5,2.5)}	&	\multicolumn{1}{c}{(2.5,1.5)}	&	\multicolumn{1}{c}{(2.5,0.5)}	&	\multicolumn{1}{c}{(1.5,1.5)}	&	\multicolumn{1}{c}{(1.5,0.5)}	&	\multicolumn{1}{c}{(0.5,0.5)}	\\ \hline
	1	&	120W	&	110W	&	90W	&	70W	&	100W	&	80W	&	60W	&	60W	&	40W	&	20W	\\ \hline
	2	&	-	&	220W	&	180W	&	140W	&	200W	&	160W	&	120W	&	120W	&	80W	&	40W	\\ \hline	3	&	-	&\textbf{330W}&	270W	&	210W	&	\textbf{300W}	&	240W	&	180W	&	180W	&	120W	&	60W	\\ \hline
4	&	-	&	-	&	-	&	-	&	-	&	\textbf{320W}	&	240W	&	240W	&	160W	&	80W	\\ \hline
	 5	&	-	&	-	&	-	&	-	&	-	&	-	&	\textbf{300W}	&	-	&	200W	&	100W	\\ \hline
	6	&	-	&	-	&	-	&	-	&	-	&	-	&	-	&	-	&	240W	&	120W	\\ \hline
\end{tabular}
\end{table*}

@@

\begin{table}[t]
% \caption{An example of the proposed method ($m = 5$)}
  \caption{}
  \centerline{AN EXAMPLE OF THE PROPOSED METHOD ($ m = 5$)}
  \vskip5pt
\begin{center}
\begin{tabular}{c|c|ccccc|c}\hline \hline
                               & \multicolumn{7}{c}{Panels}  \\
                               &  \multicolumn{1}{c}{$P1$}    & $P2$   & $P3$    & $P4$    & $P5$   & \multicolumn{1}{c}{$P6$}            & $P7$             \\ \hline
$M_{p}(Q_1)$        & 1     & 1     & 1     & 1     & 2    & 2    & 1              \\ \hline
$M_{p}(Q_2)$        & 1     & 2     & 2     & 2     & 3    & 3    & 2              \\ \hline
$M_{p}(Q_3)$        & 1     & 2     & 2     & 2     & 3    & 3    & 3              \\ \hline
$Loss(p,2)$           & 0     & 1     & 1     & 1     & 1    & 1    & 1    \\ \hline
$Loss(p,3)$           & 0     & 0     & 0     & 0     & 0    & 0    & 1    \\ \hline\hline
step 2        & $\surd$ & $\surd$ &$\surd$ &$\surd$ &$\surd$ & & \\ \hline
step 3      & $\surd$ & $\surd$ &$\surd$ & &$\surd$ & & \\ \hline
step 4       & $\surd$ &  & & &$\surd$ & $\surd$ & \\ \hline         
\end{tabular}
\end{center}
\label{tab:proposed-example}
\end{table}

@@

\begin{table}[ht]
% \caption{Swap rule}
  \caption{}
  \centerline{SWAP RULE}
  \vskip5pt
\label{tab:swap}
\centering
\begin{tabular}{c|c}
\hline\hline
\multicolumn{2}{c}{The numbers of active modules} \\
selected panels & unselected panels \\ \hline
1, 1, 1 & 3 \\ \hline
1, 1 & 2 \\ \hline
1, 2 & 3 \\ \hline
\end{tabular}
\end{table}

@@

\michiko{To evaluate the proposed method, we prepared MPP information of 100 mismatched PV arrays and applied our algorithm. We also applied an exhaustive searching algorithm for comparison.
MPP information is setup as follows for each PV array. 
Each PV array has 6 - 24  panels and the number of PV panels is randomly determined. 
Three current values are randomly assigned to the three modules in each panel from 3 - 8 current values, where the number of possible current values are also randomly determined for each PV array.
% \zhao{\large \textbf{Is that means: Current value for PV modules in each PV panel are randomly assigned from 3 - 8 current values.}}
The number of strings after reconfiguration is 3 - 6 and it is randomly determined for each PV array.}
